---
title: "Predictive distributions of performance in future studies"
---

# Goals

In a future study of 100,000 participants, what is our predictive distribution for the following:
- number individuals screened
- liver cancers detected by delfi
- liver cancers detected by ultrasound (US) + alpha fetal protein (AFP)
- false positives leading to unnecessary follow-up procedures by these approaches
- individuals with liver cancer not identified ( false negatives )

The size of the screening study is determined by the number of samples collected in a finite period of time.  Studies with lower adherence to surveillance guidelines have fewer participants.


# Best guesses

```{r packages, message=FALSE, echo=FALSE}
library(here)
library(devtools)
library(grid)
library(gridExtra)
library(gtools)
library(tidyverse)
library(mvtnorm)
library(magrittr)
library(ggplot2)
library(epiR)
library(readxl)
library(data.table)
library(patchwork)
library(cowplot)

```

```{r contours, fig.width=8, fig.height=8, dev=c("png", "pdf")}

panelA.data<-fread(here("data","LCr_contours.csv"))
pt_esti<-fread(here("data","LCr_pt_esti.csv"))
panelA <- panelA.data %>% 
    ggplot(aes(specificity, sensitivity)) +
    theme_classic(20) +
    theme(panel.grid=element_blank()) +
    geom_density2d(aes(color=tool),bins=25, size=.5) +
    scale_y_continuous(expand=c(0, 0), limits=c(0, 1)) +
    scale_x_continuous(expand=c(0, 0), limits=c(0, 1)) +
    geom_point(data=pt_esti,aes(specificity, sensitivity), size=3) + labs(color="")+
    ##xlim(c(0.15, 1)) +
    ##ylim(c(0.15, 1)) +
    ##facet_wrap(~population, ncol=1) +
    theme(strip.background=element_blank(),
          legend.position=c(0.3, 0.85)) +
    #guides(color=guide_legend(title="",
    #                          override.aes=list(size=1.5))) +
    xlab("Specificity") +
    ylab("Sensitivity")+coord_fixed()+
  scale_color_manual(values=c("darkblue","hotpink","lightpink"))#,
                     #labels=c("HE4 - 70 pM - Jacob et al., 2011","HE4 - 70 pM - JHU","CA125 - 30 U/mL - Menon et al., 2015","CA125 - 30 U/mL - JHU", "DELFI-Pro - >99% Specificity"))
panelA
#panelA <- ggplotGrob(panelA)
```




I want to plot all metrics
```{r fpr, fig.width=10, fig.height=4, dev=c("png", "pdf")}

dat<-fread(here("data","LCr_Metrics.csv"))

dat$tool<-factor(dat$tool,levels=c("Han et al, 2022 - FIB-4 > 3.25","JHU - FIB-4 > 3.25","cfDNA Fragmentome LCr Score"))


nm <- c(`npv` = "NPV",
        `TP` = "TP",
        `fnr`="FNR")

set2<-ggplot(dat,aes(x=tool,y=score,fill=tool))+geom_boxplot(outlier.shape=NA)+theme_classic(base_size=20)+
  scale_fill_manual(values=c("lightpink","hotpink","darkblue"))+xlab("")+theme(legend.position="right")+theme(axis.title = element_text(face = "bold"),
        strip.background=element_blank(),axis.text.x=element_blank(),
        axis.text.y=element_text(face = "bold"))+facet_wrap(vars(metric),nrow=1,scales="free_y",labeller = as_labeller(nm))+ylab("Performance")+labs(fill="")
set2

```


```{r}

dat %>% filter(metric=="TP") %>% group_by(tool) %>% dplyr::summarize(m=mean(score),l=quantile(score,seq(0,1,.025))[2],h=quantile(score,seq(0,1,.025))[40])

```






